---
title: "Two-Parameters"
author: "Umaira"
format: html
execute: 
  echo: false
---


```{r}
#| message: false
library(tidyverse)
library(primer.data)
library(tidymodels)
library(broom)
library(gt)
library(knitr)
```


```{r}
set.seed(10)

x <- nhanes |>
  filter(age >= 18 & age <= 27) |>
  select(height, sex) |>
  drop_na() |>
  slice_sample(n = 50) 
```
$$Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \cdots + \beta_n X_n + \epsilon$$

with $\epsilon \sim \mathcal{N}(0, \sigma^2)$.

However, this model assumes that the height differences between males and females observed in the general population from 2009-2011 remain stable and representative of future military recruits, which may not hold if recruitment patterns or population characteristics have changed over time.

$$\hat{\text{height}} = 162.18 + 15.94 \cdot \text{sexMale}$$


```{r}
#| cache: true
fit_height <- linear_reg() |> 
 fit(height ~ sex, data = x)
```

```{r}
library(knitr)

tidy(fit_height, conf.int = TRUE) |>
  select(term, estimate, conf.low, conf.high) |>
  kable(
    caption = "Estimates and 95% Confidence Intervals for Parameters\nSource: NHANES 2009–2011"
  )
```

We model height, measured in centimeters, as a linear function of sex. This linear regression approach allows us to estimate the average height difference between male and female individuals in our population of interest.
